Project Light

### 2015-09-09 paper/paper.tex
further proofreading

The Internet of Things (IoT) is becoming more and more of a reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet.
They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
E.g., motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.

@@

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
New, adapted security measurements had to be developed and implemented to react to this.
For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.

@@

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution. Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

@@

As to be seen in fig.~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
The mote receives the message via a light sensor and reconstructs the keys.
After successful initialization and verification, the mote saves the keying material permanently.
On subsequent reboots, it is read from memory and immediately usable without any further action required.

@@

The rest of the paper is structured as follows:
Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
In section~\ref{sec:communication_protocol}, we propose our protocol for the smart phone and the mote to communicate via light.
Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and it's limits.
We conclude our work and give an outlook on what could be done next in section~\ref{sec:future_work}.

>>>>

The Internet of Things (IoT) is becoming more and more of a reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet.
They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
An example are motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.

@@

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
New, adapted security measurements had to be developed and implemented to react to this.
For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack input/output devices which are securely usable without configured networking.

@@

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution. Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

@@

As visible in Figure~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
The mote receives the message via a light sensor and reconstructs the keys.
After successful initialization and verification, the mote saves the keying material permanently.
On subsequent reboots, it is read from memory and immediately usable without any further action required.

@@

The remainder of the paper is structured as follows:
Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
In section~\ref{sec:communication_protocol}, we propose our protocol for the smart phone and the mote to communicate via light.
Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and its limits.
We conclude our work and give an outlook on what could be done next in section~\ref{sec:future_work}.
